Supplementary information

### 2019-12-18 manuscript/figures.Rmd
proof figure and table captions

```{r descriptor_contributions, fig.height = 6,fig.cap = 'Descriptor importance scores from random forest models for relative contributions to\ndecline index measures. a) Phenotypic decline index (PDI). b) Decline acuteness index (DAI)'}
loadd(descriptor_contribution_plots)

@@

```{r PDI_response_surfaces,fig.height = 6,fig.cap='PDI response surfaces for simulated descriptor values from trained Random Forest models. All other descriptors were set at the values of those of the trees with the lowest PDI used for trainig the models'}
loadd(PDI_response_surfaces)

@@

```{r DAI_response_surfaces,fig.height = 8,fig.cap='DAI response surfaces for simulated descriptor values from trained Random Forest models. All other descriptors were set at the values of those of the trees with the lowest PDI used for trainig the models'}
loadd(DAI_response_surfaces)

@@

```{r DI_space,fig.cap='Two dimensional continuum of the phenotypic decline indexes for oak decline severity.',fig.height=3,fig.width=5}
DIspace()
```

>>>>

```{r descriptor_contributions, fig.height = 6,fig.cap = 'Descriptor importance scores from random forest models for relative contributions to\ndecline index measures.'}
loadd(descriptor_contribution_plots)

@@

```{r PDI_response_surfaces,fig.height = 6,fig.cap='PDI response surfaces for simulated descriptor values from trained random forest models.'}
loadd(PDI_response_surfaces)

@@

```{r DAI_response_surfaces,fig.height = 8,fig.cap='DAI response surfaces for simulated descriptor values from trained random forest models.'}
loadd(DAI_response_surfaces)

@@

```{r DI_space,fig.cap='Two dimensional continuum of the phenotypic decline indexes for oak decline severity. Decline category boundaries intended as a guide to aid interpretation only. Grey area indicates area for which the decline indexes are currently undefined.' ,fig.height=3,fig.width=5}
DIspace()
```

### 2019-12-18 manuscript/supplementary.Rmd
proof figure and table captions

```{r descriptor_adjustment,fig.cap='Exapmle of overall mean adjustment applied to the diameter at breast height descriptor. Error bars show ±1SE of the mean. Dashed red line shows the overall mean.'}
loadd(descriptor_adjustment_example)

@@

```{r site_differences,fig.cap='Differences between sites in phenotypic descriptors analysed by supervised Random Forest. a) Multidimensional scaling (MDS) plot of random forest proximity values of individual trees scaled to two dimensions. Mean margin value shown. b) Relative descriptor Gini importances measures.',fig.height=6}
loadd(site_differences_mds_plot)
grid.arrange(site_differences_mds_plot$a,site_differences_mds_plot$b,nrow = 1)
```

>>>>

```{r descriptor_adjustment,fig.cap='Exapmle of overall mean adjustment applied to the diameter at breast height (m) descriptor. Error bars show ±1SE of the mean. Dashed red line shows the overall mean.'}
loadd(descriptor_adjustment_example)

@@

```{r site_differences,fig.cap='Differences between sites in phenotypic descriptors analysed by supervised Random Forest. a) Multidimensional scaling (MDS) plot of random forest proximity values of individual trees scaled to two dimensions. Mean margin value shown. b) Descriptor importances measures.',fig.height=6}
loadd(site_differences_mds_plot)
grid.arrange(site_differences_mds_plot$a,site_differences_mds_plot$b,nrow = 1)
```
